E1 Testing - Bayesian Mixed Models

### 2023-08-14 Analysis/e1_brms_test.qmd
more bayesian tests

```{r}
pacman::p_load(tidyverse,tidybayes,brms,bayesplot,broom,broom.mixed,lme4,emmeans,here,knitr,kableExtra,gt,gghalves,patchwork,ggforce,ggdist)
e1 <- readRDS(here("data/e1_08-04-23.rds"))
source(here("Functions/Display_Functions.R"))
source(here("Functions/org_functions.R"))
test <- e1 |> 
  filter(expMode2 == "Test") |> 
  group_by(vb) |> 
  mutate(distS = as.numeric(scale(dist, scale = FALSE)), 
         distS2 = custom_scale(dist))

@@

testExtrap <- e1 |> filter(expMode=="test-Nf")

@@

## Random Effects
```{r}

modelName <- "e1_testDistRF"
e1_testDistRF <- brm(dist ~ condit + vb + (1 + vb|id),
                     data=test,file=paste0(here::here("data/model_cache",modelName)))

brms_eq_tidy <-tidyMCMC(e1_testDistRF, conf.int = TRUE, conf.level = 0.95,
           estimate.method = "median", conf.method = "HPDinterval")

bayes_R2(e1_testDistRF)
sjPlot::tab_model(e1_testDistRF)

tidyMCMC(e1_testDistRF, conf.int = TRUE, conf.level = 0.95,
           estimate.method = "median", conf.method = "HPDinterval")

(r_fit <- e1_testDistRF %>% 
  tidy() %>% filter(effect=="fixed") |> select(-effect,-component, -group) |> 
  mutate(term = janitor::make_clean_names(term)) |>
    mutate(across(where(is.numeric), \(x) round(x, 0))) |> kbl() )
```

@@

brms_eq_tidy <-tidyMCMC(e1_testDistRF2_0, conf.int = TRUE, conf.level = 0.95,
           estimate.method = "median", conf.method = "HPDinterval")

bayes_R2(e1_testDistRF2_0)
#sjPlot::tab_model(e1_testDistRF2_0)

@@

#shinystan::launch_shinystan(e1_testDistRF2_0)

@@

pp_check(e1_testDistRF2_0, type="violin_grouped",group="vb",ndraws=200)
pp_check(e1_testDistRF2_0,type = "stat_grouped", group="vb",ndraws=500)

@@

#plot(residuals(e1_testDistRF2_0))

@@

e1Test_conditBand_RS1 |> 
  spread_draws()

@@

>>>>

```{r}
pacman::p_load(tidyverse,tidybayes,brms,bayesplot,bayestestR,
               broom.mixed,lme4,emmeans,here,knitr,kableExtra,gt)
walk(c(here("Functions/Display_Functions.R"), here("Functions/org_functions.R")), source)

test <- readRDS(here("data/e1_08-04-23.rds")) |> 
  filter(expMode2 == "Test") |> 
  mutate(distS2 = custom_scale(dist))

@@

@@

## Random Effects
```{r}
#| results: asis
modelName <- "e1_testDistRF"
e1_testDistRF <- brm(dist ~ condit + vb + (1 + vb|id),
                     data=test,file=paste0(here::here("data/model_cache",modelName)))

pt <- posterior_table(e1_testDistRF) |> select(-CI)
kable(pt)
brms_posterior_checks(e1_testDistRF,dist,vb)

map_estimate(e1_testDistRF)

hdi(e1_testDistRF$fit, ci = c(0.5, 0.75, 0.89, 0.95))

plot(pt)

intPlot <- plot(conditional_effects(e1_testDistRF,effects="vb:condit"))

md <- tidy_draws(e1_testDistRF) |> select(b_Intercept:`b_vb1200M1400`)
plot(bayestestR::hdi(md, ci = c(.89, .95)))

plot(bayestestR::bayesfactor_parameters(e1_testDistRF, null = c(-.5, .5)))

p1 <- GetModelStats(e1_testDistRF)

kable(p1) |> column_spec(1:9,width="5em")

#GetBrmsModelStats(e1_testDistRF)

e1_testDistRF %>%
  spread_draws(b_Intercept, r_condition[condition,])

draws1 <- e1_testDistRF |> spread_draws()

@@

@@

@@

@@

e1_testDistRF2_0 |> spread_draws(b_conditConstant,b_conditVaried,b_vb[vb,])

e1_testDistRF2_0 |> spread_draws(r_id[id,term]) |> head(10)

e1_testDistRF2_0 |> spread_draws(b_conditConstant,b_conditVaried) |> compare_levels(condit)

@@

e1Test_conditBand_RS1 |> 
  spread_draws(b_Intercept,b_conditVaried)

@@

conditRF <- brm(vx ~ vb + condit + (1+vb|condit),data=test,iter=1000,chains=2)

conditRFX <- brm(vx ~ vb * condit + (1+vb|condit),data=test,iter=1000,chains=2,silent=0,
                 file=here("data/model_cache/e1_conditRFX"))

conditRFX %>%
  spread_draws(b_Intercept, r_condit[condit,]) %>%
  mutate(condition_mean = b_Intercept + r_condit) %>%
  ggplot(aes(y = condit, x = condition_mean)) +
  stat_halfeye() + facet_wrap(~vb)
